Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-01-20 paper.tex
Spelling fixes, etc.

\todo{edit start}
The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones.
Both these devices are shown in \cref{fig:tango-headphone}.
This a Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.
\todo{edit end}

@@

\todo{edit start}
This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source 3D positions.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
\todo{edit stop}
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Over multiple years, both commercial and academic parties have devices new and innovative mobile navigation and travel aids for people with visual impairments.
Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with significant resolution.
Furthermore, both haptic and vocal feedback can present a significant cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if the tone is too unpleasant.
Researchers started using cameras and object detectors to determine what a user is looking at and using them together with simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

@@

Work has been done in an attempt to add complexity to these tones by spatialising them with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
The authors generally report favourable results when using snormal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
However, the audio transmission device used has a significant effect on performance.
Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization}.
However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as the work by~\citet{durette2008visuo}.
We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}.
We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive and over-ear headphones.

@@

\subsection{Participant Feedback}

\todo{include subjective feedback?}

>>>>

The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones.
Both of these devices are shown in \cref{fig:tango-headphone}.
This Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.

@@

This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Over the years, commercial and academic parties have devised new and innovative mobile navigation and travel aids for people with visual impairments.
Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, both haptic and vocal feedback can present a significant cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
Indeed, participants report that they prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

@@

Work has been done in an attempt to add complexity to these tones by spatialising them with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
However, the audio transmission device used has a significant effect on performance.
Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization}.
However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}.
We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive over-ear headphones.

@@

%\subsection{Participant Feedback}

%\todo{include subjective feedback?}
